---
title: "A3: SPL Library Checkouts from Rick Riordan"
output: html_document
---

### Introduction

The data I am analyzing is from the Seattle Public Library pertaining to all the items checked out within the past year of 2022-2023. I decided to explore the trends of one of my favorite authors, Rick Riordan. He is the creator of the Percy Jackson series, Heroes of Olympia, Kane Chronicles, etc. I decided to look into his books because growing up reading works really helped me grow as a person. I am curious to see if he is still popular today as he was when I was a child. 

### Summary Information

This Rick Riordan dataset contains a total of 282 unique book titles. The total number of checkouts of only titles by Rick Riordan is 169871. The year with the most checkouts of titles by Riordan was 2012. The title with the most checkouts was a physical book called “The Mark of Athena” with 177 checkouts in one month.

### The Dataset

The data was collected and published by the Seattle Public Library. The data is up to a recent date as of February 21, 2023. It contains the number of checkouts, the subjects, the checkout year and month, usage classification, type of checkout, material type, publisher, ISBN, and titles. The data was generated with the [SPL Open Data Portal](https://data.seattle.gov/Community/Checkouts-by-Title/tmmm-ytt6/explore/query/SELECT%0A%20%20%60usageclass%60%2C%0A%20%20%60checkouttype%60%2C%0A%20%20%60materialtype%60%2C%0A%20%20%60checkoutyear%60%2C%0A%20%20%60checkoutmonth%60%2C%0A%20%20%60checkouts%60%2C%0A%20%20%60title%60%2C%0A%20%20%60isbn%60%2C%0A%20%20%60creator%60%2C%0A%20%20%60subjects%60%2C%0A%20%20%60publisher%60%2C%0A%20%20%60publicationyear%60/page/filter). The data was collected so I could analyze trends with a specific author, Rick Riordan, at the Seattle Public Library. 

Some possible limitation of this data is that there are authors who republish Riordans work under their name, such as a graphic novel adaptation. Even though he is the creator of the source material, he is not mentioned in the creator column of the data. I believe these limitations will not fully account for Riordan’s influence and popularity. 



### Paperbooks, Ebooks, and Audiobooks

``````{r, echo = FALSE, code = readLines("Chart1.R"), warning = F, message = F}
``````




### Average Checkouts over the Months


``````{r, echo = FALSE, code = readLines("Chart2.R"), warning = F, message = F}
``````

### Rick Riordan's Top 5 Titles

``````{r, echo = FALSE, code = readLines("Chart3.R"), warning = F, message = F}
``````


