---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

The data I am analyzing is from the Seattle Public Library pertaining to all the items checked out within the past year of 2022-2023. I decided to explore the trends of one of my favorite authors, Rick Riordan. He is the creator of the Percy Jackson series, Heroes of Olympia, Kane Chronicles, etc. I decided to look into his books because growing up reading works really helped me grow as a person. I am curious to see if he is still popular today as he was when I was a child. 

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

The data was collected and published by the Seattle Public Library. The data is up to a recent date as of February 21, 2023. It contains the number of checkouts, the subjects, the checkout year and month, usage classification, type of checkout, material type, publisher, ISBN, and titles. The data was generated with the [SPL Open Data Portal](https://data.seattle.gov/Community/Checkouts-by-Title/tmmm-ytt6/explore/query/SELECT%0A%20%20%60usageclass%60%2C%0A%20%20%60checkouttype%60%2C%0A%20%20%60materialtype%60%2C%0A%20%20%60checkoutyear%60%2C%0A%20%20%60checkoutmonth%60%2C%0A%20%20%60checkouts%60%2C%0A%20%20%60title%60%2C%0A%20%20%60isbn%60%2C%0A%20%20%60creator%60%2C%0A%20%20%60subjects%60%2C%0A%20%20%60publisher%60%2C%0A%20%20%60publicationyear%60/page/filter). The data was collected so I could analyze trends with a specific author, Rick Riordan, at the Seattle Public Library. 

Some possible limitation of this data is that there are authors who republish Riordans work under their name, such as a graphic novel adaptation. Even though he is the creator of the source material, he is not mentioned in the creator column of the data. I believe these limitations will not fully account for Riordan’s influence and popularity. 



### Paperbooks, Ebooks, and Audiobooks

``````{r, echo = FALSE, warning = FALSE, code = readLines("Chart1.R"), warning = F, message = F}
```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```


